Study 1 Analysis

### 2024-10-26 study1.qmd
add new design + stimuli page, and re-render all sites. s1 also has some new data checks for the state freq oddities.

s1 <- s1 |> 
  mutate(change = value-family, state_dif = value-state_avg,calc = if_else(calc == 0, "No Calculator", "Used Calculator")) |> 
  mutate(value=as.numeric(value))

@@

s1_agg <- s1 |> 
  filter(appliance !="Total kWh") |> 
  group_by(id,refClass,state,block,plan,calc,edu,pct_goal) |> 
  summarise(total_kWh = sum(value),orig_kWh=sum(family), pct_change = round((orig_kWh-total_kWh)/orig_kWh,3), state_dif=mean(state_dif)) |> 
  mutate(matched_goal = (pct_change == pct_goal))

@@

@@

>>>>

s1 <- s1 |> 
  mutate(change = value-family, 
         state_p_dif = value-state_avg,
         state_f_dif= family-state_avg,
         less_avg = value<state_avg,
         calc = if_else(calc == 0, "No Calculator", "Used Calculator")) |> 
  mutate(value=as.numeric(value))

@@

s1_agg <- s1 |> 
  filter(appliance !="Total kWh") |> 
  group_by(id,refClass,state,block,plan,calc,edu,pct_goal) |> 
  summarise(total_kWh = sum(value),orig_kWh=sum(family), 
            pct_change = round((orig_kWh-total_kWh)/orig_kWh,3), 
            n_change = sum(value!=family),
            state_p_dif=mean(state_p_dif),
            state_f_dif=mean(state_f_dif),
            n_less_avg = sum(less_avg)) |> 
  mutate(matched_goal = (pct_change == pct_goal))

@@

# plot frequency dist of values of n_change
s1_agg |> ggplot(aes(x=n_change)) +
  geom_bar(fill = 'dodgerblue4',width=1) +
  theme_minimal()

# examine relationship between n_change and whether goal was matched
s1_agg |> ggplot(aes(x=n_change,fill=matched_goal)) +
  geom_bar(position="dodge") +
  theme_minimal() +
  labs(title="Relationship between # of changes and whether goal was matched",
       x="# of changes",
       y="Count") +
  scale_fill_brewer(palette="Set2")

# alternative way to examine the relationship, not a plot
s1_agg |> group_by(n_change,matched_goal) |> summarise(n=n()) |> 
  gt() |> tab_header(title="Relationship between # of changes and whether goal was matched")

s1 |> 
  filter(appliance !="Total kWh") |> 
  group_by(state, appliance) |> 
  summarise(family=mean(family),state_avg=mean(state_avg),dif=family-state_avg)

s1 |> ungroup() |> mutate(diff=family-state_avg) |> group_by(state,appliance) |>  summarize(min(diff))

s1 |> ungroup() |> mutate(diff=family-state_avg) |> group_by(state) |> filter(diff<0) |> select(id,state1,state2,state,appliance,family,state_avg,plan,value,diff)

# examine the relationship between n_less_avg (a value btw 0 and 5) and whether goal was matched
s1_agg |> ggplot(aes(x=n_less_avg,fill=matched_goal)) +
  geom_bar(position="dodge") +
  facet_wrap(~state) +
  theme_minimal() +
  labs(title="Relationship between # of appliances changed to below state average and whether goal was matched",
       x="# of appliances changed to below state average",
       y="Count") +
  scale_x_continuous(breaks=seq(1,5,1))

@@

## Data checks

library(tidyverse)

# for every combination of state, appliance, and refClass, calculate the number of distinct values of family, and of state_avg
s1 |> group_by(state,appliance,refClass) |> 
  summarise(n_distinct_family=n_distinct(family),
            n_distinct_state_avg=n_distinct(state_avg), 
            # paste a string of each distinct value, separated by a comma
            distinct_family=paste(unique(family),collapse=","),
            distinct_state_avg=paste(unique(state_avg),collapse=",")) |>
  filter(n_distinct_family>1 | n_distinct_state_avg>1)

s1 |> group_by(state,appliance,refClass) |> 
  mutate(n_distinct_family=n_distinct(family),
            n_distinct_state_avg=n_distinct(state_avg), 
            # paste a string of each distinct value, separated by a comma
            distinct_family=paste(unique(family),collapse=","),
            distinct_state_avg=paste(unique(state_avg),collapse=",")) |>
  filter(n_distinct_family>1 | n_distinct_state_avg>1) |> 
  group_by(state,appliance,refClass,family,state_avg) 
  # the count of each unique value of family, and each unique value of state avg

s1 |> 
    group_by(state, appliance, refClass) |> 
    mutate(n_distinct_family = n_distinct(family),
           n_distinct_state_avg = n_distinct(state_avg), 
           distinct_family = paste(unique(family), collapse = ","),
           distinct_state_avg = paste(unique(state_avg), collapse = ",")) |>
    filter(n_distinct_family > 1 | n_distinct_state_avg > 1) |> 
    group_by(state, appliance, refClass, family, state_avg) |> 
    mutate(state_avg_count = n_distinct(state_avg),
           family_count = n()) |> 
    ungroup() |> 
    group_by(state, appliance, refClass, state_avg) |> 
    mutate(state_avg_count = n()) |> 
    distinct(state, appliance, refClass, family, state_avg, family_count, state_avg_count) |> 
  arrange(state,appliance,refClass)

haven::read_sav(here::here("data/Frequency & Probability Study 1 - 3-24-19.sav"))  |> filter(ResponseId=="R_2QMsYuHS385pTj1") -> k
# find if any columns equal 5.26

haven::read_sav(here::here("data/Frequency & Probability Study 1 - 3-24-19.sav"))  |> select_if(~any(. ==11441.0)) |> 
  # filter out any NAs from any column that is left (we don't know the column names)
  filter_all(any_vars(!is.na(.))) |> 
  # retain only cases of 11441.0
  filter_all(any_vars(. == 11441.0))

haven::read_sav(here::here("data/Frequency & Probability Study 1 - 3-24-19.sav"))  |> # return the names of any columns that contain 11441.0
  select_if(~any(. ==11441.0)) |> 
  names() |> 
  str_c(collapse=",") |> 
  cat() # P3TEX15

# do the same procedure for each of these values, include a line break after the output from each number
low_freq <- c(5.26, 4534, 340,11667,5.3,400, 29046,5600,5987,34265.0,5600.0	)

# for(val in low_freq) {
#   haven::read_sav(here::here("data/Frequency & Probability Study 1 - 3-24-19.sav")) |>
#     select_if(~any(. == val)) |>
#     names() |>
#     str_c(collapse = ",") |>
#     cat()
#   cat("\n")  # Add line break after each output
# }

low_freq |>
  walk(function(val) {
    cat(val, "\n")  # Print the current value
    haven::read_sav(here::here("data/Frequency & Probability Study 1 - 3-24-19.sav")) |>
      select_if(~any(. == val)) |>
      names() |>
      str_c(collapse = ",") |>
      cat()
    cat("\n\n")  # Add two line breaks before next value
  })

k %>% select_if(~any(is.numeric(.)) & . <10)
haven::read_sav(here::here("data/Frequency & Probability Study 1 - 3-24-19.sav")) |> select(P3TEX15) |> unique()

haven::read_sav(here::here("data/Frequency & Probability Study 1 - 3-24-19.sav")) |> 
  #select(ResponseId, P3TEX15) |> 
  filter(!is.na(P3TEX15))

# A tibble: 2 × 2
#   P3TEX15 `n()`
#     <dbl> <int>
# 1    5.26    10
# 2   NA      242
